---
title: "Shiny Application - Prediction Model for Motor Trend Car Road Tests"
author: "DomoM"
date: "10/30/2020"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Introduction

Write a shiny application with associated dataset from Motor Trend Car Road Tests ("mtcars"). The interactive webpage provides a simple operation to predict the horsepower w.r.t. mpg (tab 1) and mpg w.r.t. cars' weight (tab 2) using linear regression modeling. 

## Dataset for Motor Trend Car Road Tests

```{r, echo=FALSE, fig.align='center', message=FALSE, warning=FALSE}
str(mtcars)
```

## How to Use the Interactive Box

### Tab 1: input a number within the given range in the box1 for a mpg value to predict the horsepower.

### Tab 2: input a number within the given range in the box2 for a weight value to predict the mpg.

## Plots Demo

```{r, echo=FALSE, fig.align='center', message=FALSE, warning=FALSE}
    #build the model to predict horsepower from pmg
    model1<-lm(hp~mpg, data=mtcars)
    mpgInput1<-20
    model1pred <- predict(model1,newdata=data.frame(mpg=as.numeric(mpgInput1)))
    
    #build the model to predict mph from wt
    model2<-lm(mpg~wt, data=mtcars)
    mpgInput2<-3
    model2pred<-predict(model2, newdata=data.frame(wt=as.numeric(mpgInput2)))
    
    par(mfrow=c(1,2))
    plot(mtcars$mpg, mtcars$hp, xlab="miles per gallon", ylab="horsepower", 
         main="Tab 1", pch=16)
    abline(model1, col="red",lwd=1)
    legend("topright", pch=3, legend=c("model prediction"), col=c("red"))
    points(mpgInput1, model1pred, col = "red", pch=16, cex=2)
       
    plot(mtcars$wt, mtcars$mpg, xlab="weight (/1000 lbs)", 
                ylab="miles per gallon", main="Tab 2", pch=16)
    abline(model2, col="blue",lwd=1)
    legend("topright", pch=1, legend=c("model prediction"), col=c("blue"))
    points(mpgInput2, model2pred, col = "blue", pch=16, cex=2)
```
